Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-18 cordillera-cycle.tex
Add grid lines on timeseries plots.

% fig:timeseries
\begin{figure*}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and sediment core
           records (Table~\ref{tab:records}) used as palaeo-climate forcing for
           the ice sheet model \textbf{(top)}, and modelled ice volume
           through the last 120\,kyr, expressed in meters of sea-level
           equivalent \textbf{(bottom)}. Gray spans indicate Marine Isotope
           Stages (MIS) according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{Lisiecki.Raymo.2005}. Hatched
           rectangles highlight modelled ice volume extrema corresponding to
           MIS~4 (61.9--55.4\,kyr), MIS~3 (52.2--45.6\,kyr), and
           MIS~2 (last glacial maximum, 29.5--16.9\,kyr). Dotted lines
           correspond to the GRIP and EPICA 6\,km-resolution runs.
           \todo{add grid lines to improve readability}}
  \label{fig:timeseries}
\end{figure*}

@@

% fig:deglacseries
\begin{figure}
  \includegraphics{deglacseries}
  \caption{Temperature offset time-series from the GRIP and EPICA ice core
           records (Table~\ref{tab:records}) \textbf{(top)}, and modelled ice
           volume during the deglaciation, expressed in meters of sea-level
           equivalent \textbf{(bottom)}.
           \todo{add grid lines to improve readability}}
  \label{fig:deglacseries}
\end{figure}

>>>>

% fig:timeseries
\begin{figure*}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and sediment core
           records (Table~\ref{tab:records}) used as palaeo-climate forcing for
           the ice sheet model \textbf{(top)}, and modelled ice volume
           through the last 120\,kyr, expressed in meters of sea-level
           equivalent \textbf{(bottom)}. Gray spans indicate Marine Isotope
           Stages (MIS) according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{Lisiecki.Raymo.2005}. Hatched
           rectangles highlight modelled ice volume extrema corresponding to
           MIS~4 (61.9--55.4\,kyr), MIS~3 (52.2--45.6\,kyr), and
           MIS~2 (last glacial maximum, 29.5--16.9\,kyr). Dotted lines
           correspond to the GRIP and EPICA 6\,km-resolution runs.}
  \label{fig:timeseries}
\end{figure*}

@@

% fig:deglacseries
\begin{figure}
  \includegraphics{deglacseries}
  \caption{Temperature offset time-series from the GRIP and EPICA ice core
           records (Table~\ref{tab:records}) \textbf{(top)}, and modelled ice
           volume during the deglaciation, expressed in meters of sea-level
           equivalent \textbf{(bottom)}.}
  \label{fig:deglacseries}
\end{figure}
